Figures for Paper

### 2021-03-09 paper_figures.Rmd
updated script
added script to create nmd plot in dz cells (sup fig 2b)

>>>>

for_bar_plot_dz <- read_csv(file.path(here::here(),"data","results_17022021_dz.csv"))

for_bar_plot_dz <- data.frame(for_bar_plot_dz)
for_bar_plot_dz$condition <- as.factor(for_bar_plot_dz$condition)
for_bar_plot_dz$condition <- factor(for_bar_plot_dz$condition,levels(for_bar_plot_dz$condition)[c(2,1)])

nmd_plot2 = ggbarplot(for_bar_plot_dz,
                        x = 'gene',
                        add = c("mean_se","jitter"),
                        y = 'value',
                        fill = 'condition',
                        color = 'condition',
                        position = position_dodge(0.8),
                        dot.size = 10) + 
  scale_y_continuous(labels = scales::percent) + 
  ggpubr::theme_pubr() +
  scale_fill_manual(
    values = c("#40B0A6","#E1BE6A")
  ) + 
  scale_color_manual(
    values = c("#1C2617","#262114")
  )

plot(nmd_plot2)
```
